# Strain tracking hackaton

With the previous exemplary commands you have familiarized yourself little bit with bioinformatics part of metagenomics. In the the second session we will try to apply these functions to identify a microbe which has come from the donor and engrafted in a metsyn patient.

You will need to trade of speed with sensitivty, what would be your approach?
Tip; try to reduce your dataset and search space by using fast tools before applying sensitive tools.

# 

I will update this page during the hackaton with to help with examples 

Fastq files can be found here:
/media/data/rawdata/fastqfiles/


Background information 
https://github.com/biobakery/MetaPhlAn/wiki/StrainPhlAn-4.1

My first approach would be to identify likely engrating strains:

```{r, eval=F, class.source='klippy'}
mamba activate /media/data/shared_conda_environments/kraken2/
```

replace samples and output  with correct files

```{r, eval=F, class.source='klippy'}
mkdir ~/Results/kraken2/

kraken2 --db /dev/shm/kraken/ \
--memory-mapping \
--threads 12 \
--classified-out ~/Results/kraken2/example.classified.#.fq \
--unclassified-out ~/Results/kraken2/example.unclassified.#.fq \
--paired ~/Results/trimmed_reads/example.trimmed.R1.fq.gz ~/Results/trimmed_reads/example.trimmed.R2.fq.gz \
--report ~/Results/kraken2/example.report \
--confidence 0.01 \
--use-names > ~/Results/kraken2/example.read.results
```


Knowing this data was from the published FMT set, Prevotella, Collinsella etc are likely candidates.
With this knowledge you could have started strainphlan out of the gates.

```{r, eval=F, class.source='klippy'}
mkdir -p sams
mkdir -p bowtie2
mkdir -p profiles
for f in /media/data/rawdata/fastqfiles/*R1* ; do     echo "Running MetaPhlAn on ${f}";     bn=$(basename ${f});     metaphlan ${f} --input_type fastq -s sams/${bn}.sam.bz2 --bowtie2out bowtie2/${bn}.bowtie2.bz2 -o profiles/${bn}_profiled.tsv --bowtie2db /media/data/database/biobakery/; done
```

SGB table:

https://opendata.lifebit.ai/table/SGB



